\thetitle

### 2023-04-19 frontmatters.tex
Update statement of contributions.

Ende Jin and Prof. Yizhou Zhang co-authored Chapter 1.

Ende Jin is the sole author of Chapter 2, which were written under the  under the supervision of Prof. Yizhou Zhang.

Both Chapter 1 and Chapter 2 are already published result.

\noindentparagraph{Research presented in Chapter 1 and 2:} Ende Jin is the primary investigator of both theoretical development and practical implementation of the prototype. This work was supported in part by an Amazon research award on automated
reasoning.

>>>>

Ende Jin is the sole author of \cref{sec:metatheory2}, which were written under the under the supervision of Prof. Yizhou Zhang.

Ende Jin and Prof. Yizhou Zhang co-authored the rest of the thesis.

This thesis is a published result.

\noindentparagraph{Research presented in the thesis:} Ende Jin is the primary investigator of both theoretical development and practical implementation of the prototype. This work was supported in part by an Amazon research award on automated
reasoning.
